\documentclass{article}

\usepackage{hyperref}
\usepackage{sectsty}
\sectionfont{\huge\sc}
\subsectionfont{\LARGE\sc}
\subsubsectionfont{\large}
\usepackage{fullpage}

\begin{document}
\section*{Duncan Macleod}

\hrule \vspace{5mm}

\subsection*{Contact Information}
\begin{center}
\begin{tabular}{ll}
\textbf{Postal Address:} & \textbf{Work Address:} \\
Flat 3, 14 The Walk & School of Physics and Astronomy\\
Roath & Queen's Buildings\\
Cardiff & Cardiff University\\
Wales & Cardiff \\
United Kingdom & Wales\\
CF24 3AF & United Kingdom\\
& CF24 3AA \\
\\
\multicolumn{2}{l}{\textbf{E-mail:}
\href{mailto:duncan.macleod@astro.cf.ac.uk}{duncan.macleod@astro.cf.ac.uk}}\\
\textbf{Home Tel:} +44(0) 2920 313654\\
\textbf{Office Tel:} +44(0) 2920 875120\\
\textbf{Mob:} +44(0) 7971 743808\\
\end{tabular}
\end{center}

\subsection*{Profile} 
First year postgraduate student looking to gain experience in the field of gravitational waves including data analysis techniques and detector characterisation.

\subsection*{Education}
\subsubsection*{September 2009 -- Present: Cardiff University}
PhD (research) with the Gravitational Waves group (School of Physics and Astronomy) in data analysis searching for gravitational wave signals from compact binary coalescence.

\paragraph{Research interests:} The theory and detection of gravitational waves using current enhanced and future advanced detectors, including data analysis searching for compact binary coalescence and improving detector characterisation. I am also interested in working towards the third generation gravitational wave detectors, specifically the Einstein Telescope project.

\subsubsection*{September 2004 -- June 2009: The University of Edinburgh}
Master of Physics in Mathematical Physics. First class Honours.
\begin{itemize}
\item Masters Project: Introduction to the theory of gravitational radiation and parameter estimation from compact binary coalescence.
\item Supervisor: Dr. Luigi Del Debbio
\end{itemize}
\paragraph{Courses Included:}
\begin{center}
\begin{tabular}{lll}
$\bullet$ Astrophysical Cosmology & $\bullet$ General Relativity & $\bullet$ Particle Physics \\ $\bullet$ Relativistic Quantum Field Theory & $\bullet$ The Standard Model & $\bullet$ Statistical Physics
\end{tabular}
\end{center}

\subsubsection*{1998--2004: Gryffe High School, Renfrewshire, UK}
\begin{minipage}{3in}
\paragraph{SQA Advanced Higher results 2004}
\begin{center}
\begin{tabular}{ll}
Mathematics & A\\
Music & A\\
Physics & A \\
\end{tabular}
\end{center}
\end{minipage}
\begin{minipage}{3in}
\paragraph{SQA Higher results 2003}
\begin{center}
\begin{tabular}{llll}
Computing & A & Economics & A \\
English & A & Mathematics & A \\
Music & A & Physics & A
\end{tabular}
\end{center}
\end{minipage}

\subsection*{Work Experience}
\paragraph{September 2009 -- Present: Marker and Demonstrator, School of Physics and Astronomy, Cardiff University.} Postgraduate internal work as a demonstrator for a first year undergraduate computing module, and a marker for an first year undergraduate mathematics for physical scientists module.

\paragraph{June 2004 -- January 2010 (part-time): Musician, Highland Band of the Royal Regiment
of Scotland (TA).} Working under a military rank system while
performing at musical events has combined the need for creativity
and technical ability with discipline, organisation and teamwork.

\subsection*{Interests}
Most of my time outside of study is spent on music. Having played
the trumpet since the age of 10 I have been involved
in multiple musical group within Edinburgh, as principal trumpet of the University Symphony Orchestra, for four years, and in \textit{Scottish Sinfonia}, and more recently in Cardiff, as principal trumpet of both the University Symphony Orchestra and Chamber Orchestra.

\subsection*{References}
\begin{center}
\begin{tabular}{lll}
Dr. Patrick Sutton & Dr. Stephen Fairhurst & Prof. B. S. Sathyaprakash \\
School of Physics and Astronomy & School of Physics and Astronomy & School of Physics and Astronomy \\
Cardiff University & Cardiff University & Cardiff University\\
Queen's Buildings &  Queen's Buildings & Queen's Buildings\\
The Parade & The Parade & The Parade\\
Cardiff & Cardiff & Caridff\\
CF24 3AA & CF24 3AA & CF24 3AA\\
+44(0)2920 874649 & +44(0)2920 870166 & +44(0)2920 876962\\
\href{mailto:patrick.sutton@astro.cf.ac.uk}{patrick.sutton@astro.cf.ac.uk} & \href{mailto:stephen.fairhurst@astro.cf.ac.uk}{stephen.fairhurst@astro.cf.ac.uk} & \href{mailto:b.sathyaprakash@astro.cf.ac.uk}{b.sathyaprakash@astro.cf.ac.uk}
\end{tabular}
\end{center}

\end{document}